\vspace{-0.25em}\thetitle

### 2009-07-31 paper.tex
...

Our results show that we can predict the packet size distribution, inter-packet interval distribution, and packet count distribution of flows from only a handful of initial packets of each flow.
Specifically, we have used five initial packets to predict these distributions with between 70\% and 90\% accuracy across a wide variety of network traces.
Moreover, about half of the time, we can reduce our uncertainty about the number of packets that flows will have by 80\% or more.
Immediate applications of this ability to accurately predict individual flow behaviors abound.
Quality of service (\caps{QoS}) schemes attempting to provide high-quality service guarantees for streaming voice and video wireless through wireless networks could use such predictions to know, almost presciently, how much data flows are likely to transmit and how often.
Routers could use information about data rates from these predictions to load-balance across multiple possible routes towards their ultimate destinations.

@@

The numerical techniques needed to tackle non-parametric mixture modeling have only very recently become available.
In our model recovery procedure, we use a subspace segmentation algorithm published in 2007~\cite{Ma07}, two \caps{NMF} algorithms published in 2001 and 2008, respectively~\cite{Lee01,Kim08:anls}, and a low-rank \caps{NMF} initialization technique published for the first time here.
All of these techniques are still quite immature:
New \caps{NMF} algorithms have been regularly proposed since Lee and Seung's seminal paper in 2001.
Their algorithms are still the most well-known, and often the most reliable despite their various shortcomings~\cite{Langville06}.
they will only improve over time, yielding even better recovery of the model parameters.
Such improvements will immediately improve the performance of the prediction methods employed in this paper.

>>>>

The results demonstrate that we can predict the packet size distribution, inter-packet interval distribution, and packet count distribution of flows from only a handful of initial packets of each flow.
Specifically, we have used five initial packets to predict these distributions with between 70\% and 90\% accuracy across a wide variety of network traces.
Moreover, about half of the time, we can reduce our uncertainty about the number of packets that flows will have by 80\% or more.
Immediate applications of this ability to accurately predict individual flow behaviors abound.
Quality of service (\caps{QoS}) schemes attempting to provide high-quality service guarantees for streaming voice and video wireless through wireless networks could use such predictions to know, almost presciently, how much data flows are likely to transmit and how often.
Routers could use information about data rates from these predictions to load-balance across multiple possible routes towards their ultimate destinations.

@@

The numerical techniques needed to tackle non-parametric mixture modeling have only very recently become available.
In our model recovery procedure, we use a subspace segmentation algorithm published in 2007~\cite{Ma07}, two \caps{NMF} algorithms published in 2001 and 2008, respectively~\cite{Lee01,Kim08:anls}, and a low-rank \caps{NMF} initialization technique published for the first time here.
All of these techniques are still quite immature:
New \caps{NMF} algorithms have been regularly proposed since Lee and Seung's seminal paper in 2001.
Their algorithms are still the most well-known, and often the most reliable despite their various shortcomings~\cite{Langville06}.
These algorithms will only improve over time, yielding better recovery of model parameters.
Such improvements will immediately improve the performance of the prediction methods employed in this paper.
